Verifying Demonstrations

### 2018-05-30 paper/RelatedWork.tex
expand requirements in conclusion, leave related work

Trusted infrastructure, for example deployed by a collection of  media outlets ~\cite{LeMondeProtestingSolution}, is another recent development, but without verfiability of privacy guarantees.

>>>>

Trusted infrastructure, for example deployed by a collection of  media outlets ~\cite{LeMondeProtestingSolution}, is another recent development, but without verfiability or privacy guarantees.
